#install.packages('flexdashboard')
#install.packages("plotly")


#file-->new file-->R markdown-->template-->flex
#To see this output we need to "Knit" the file by either clicking on the 
#Knit icon near the top of our faile or pressing Ctrl+Shift+K.



#We could have a one-page dashboard but that would mean cramming a lot of 
#information in a small space. Flexdashboard gives us an option for having 
#multiple pages on our dashboard by demarcating sections in the code using the === header



#Now within a page, the layout orientation is based on rows or columns (or both). 
#A new row or column can be added using the ---header or ##.



#In R markdown working code needs to be encapsulated by the delimiters ```r{} and ``` 
#also called the code chunk delimiters. The way R markdown works is it will embed the 
#results at the end of the code chunk onto the HTML dashboard output.



#ValueBox: Sometimes you want to include one or more simple values within a dashboard. 
#You can use the valueBox function to display single values along with a title and 
#optional icon.
#You can specify icons from three different icon sets:
#Font Awesome
#Ionicons
#Bootstrap Glyphicons
#When referring to an icon you should use it's full name including the icon set 
#prefix (e.g. "fa-github", "ion-social-twitter", "glyphicon-time", etc.).



#Linking
#If a valueBox displays a value for which additional detail is available on another 
#dashboard page you can enable navigation to the other page via the href parameter.



#Gauges: Gauges display values on a meter within a specified range.



---
  title: "iris"
output: 
  flexdashboard::flex_dashboard:
  orientation: column #change this to row
vertical_layout: scroll #fill/scroll
---
  
  
  
  ```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```
Page 1
===
  Column {data-width=650}
-----------------------------------------------------------------------
  
  
  
  ### Chart A
  
  
  
  ```{r}



```



Page 2
===
  Column {data-width=350}
-----------------------------------------------------------------------
  
  
  
  ### Chart B
  
  
  
  ```{r}



```



### Chart C



```{r}



```
Page 3
===
  Column {data-width=350}
-----------------------------------------------------------------------
  
  
  
  ### Chart D
  
  
  
  ```{r}



```



### Chart E



```{r}



```



### Chart F



```{r}



```



Page 4 {data-orientation=rows}
===
  Row {data-height=650}
-------------------------------------
  
  ### Chart 1
  
  ```{r}



```

Row {data-height=350}
-------------------------------------
  
  ### Chart 2
  
  ```{r}



```

### Chart 3



```{r}



```



Page 5
===
  Column {data-width=600}
-------------------------------------
  
  ### Chart 1
  
  ```{r}



```

Column {data-width=400}
-------------------------------------
  
  ### Chart 2
  
  
  
  ```{r}



```   

### Chart 3

```{r}



```
Page 6 {data-icon="fa-hashtag"}
===
  Column 
-------------------------------------
  
  ### Chart 1
  
  ```{r}



```

Column {.tabset}
-------------------------------------
  
  ### Chart 2
  
  
  
  ```{r}



```   

### Chart 3

```{r}



```
Page 7 {data-orientation=rows}
===
  Row 
-------------------------------------
  
  ### Chart 1
  
  ```{r}



```

Row {.tabset .tabset-fade}
-------------------------------------
  
  ### Chart 2
  
  
  
  ```{r}



```   

### Chart 3

```{r}



```



Page 8 {data-orientation=rows}
===
  Row
-----------------------------------------------------------------------
  
  
  
  ### Articles per Day
  
  
  
  ```{r}
valueBox(45, icon = "fa-pencil", href="#details")
```



### Comments per Day



```{r}
valueBox(126, icon = "fa-comments")
```



### Spam per Day



```{r}
spam <- 5
valueBox(spam, 
         icon = "fa-trash",
         color = ifelse(spam > 10, "warning", "primary"))
```